UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-14 files/paper/paper.tex
update

\usepackage{graphicx}
\graphicspath{ {images/}{images/figure1/} }
%\graphicspath{{images/failures/}}
%\graphicspath{{images/figure1/}}

@@

@@

   \small{Original} & \small{CycleGAN} & \small{UGAN} & \small{UGAN-P} \\

@@

>>>>

\usepackage{graphicx}
\graphicspath{ {images/}{images/figure1/}{images/figure2/}{images/figure3/} }
%\graphicspath{{images/failures/}}
%\graphicspath{{images/figure1/}}

@@

% TODO definitely need help with formatting, but content is there
\begin{figure*}
\centering
\begin{tabular}{p{4.0cm} p{4.0cm} p{4.0cm} p{4.0cm}}

   \includegraphics[width=1.7in]{flickr_cmp} &
   \includegraphics[width=1.7in]{cgan_cmp} &
   \includegraphics[width=1.7in]{ugan_cmp} &
   \includegraphics[width=1.7in]{uganp_cmp} \\

\end{tabular}
\end{figure*}
\begin{figure*}
\begin{tabular}{p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} p{1.9cm} }

   \includegraphics[width=0.8in]{flickr_crop1} &
   \includegraphics[width=0.8in]{flickr_crop2} &
   \includegraphics[width=0.8in]{cgan_crop1} &
   \includegraphics[width=0.8in]{cgan_crop2} &
   \includegraphics[width=0.8in]{ugan_crop1} &
   \includegraphics[width=0.8in]{ugan_crop2} &
   \includegraphics[width=0.8in]{ugan_crop1} &
   \includegraphics[width=0.8in]{ugan_crop2} \\

   \includegraphics[width=0.8in]{flickr_crop3} &
   \includegraphics[width=0.8in]{flickr_crop4} &
   \includegraphics[width=0.8in]{cgan_crop3} &
   \includegraphics[width=0.8in]{cgan_crop4} &
   \includegraphics[width=0.8in]{ugan_crop3} &
   \includegraphics[width=0.8in]{ugan_crop4} &
   \includegraphics[width=0.8in]{ugan_crop3} &
   \includegraphics[width=0.8in]{ugan_crop4} \\

\end{tabular}
\caption{Zooming in on comparisons.}
\end{figure*}

@@

   5 \small{Original} & \small{CycleGAN} & \small{UGAN} & \small{UGAN-P} \\

@@

Future work: Getting a better and larger dataset. I think that would help a great deal. Also data augmentation
after CycleGAN, such as gaussian blurring, noise, particle effect, more lighting effects etc.
